\newglossaryentry{heidler}
{
    name=Heidler function,
    description={A function used to generate lightning impulse currents. There are several parameters that can be changed to manipulate the rise and fall times of the waveshape. This function is stipulated in the IEC~62305-1 standard as the standardised lightning impulse current model used for Lightning Protection System design.}
}
\newglossaryentry{approx}
{
    name=Heidler function approximation,
    description={The function developed in this dissertation that approximates the Hediler function with an analytical integral.}
}
\newglossaryentry{waveshape}
{
    name=Waveshape,
    description={The shape of a graph in the time domain.}
}
\newglossaryentry{iec}
{
    name=IEC~62305,
    description={The lightning protection standard.}
}
\newglossaryentry{iec1}
{
    name=IEC~62305-1,
    description={Part one of the IEC~62305. This details all the parameters of lightning currents and the nomenclature used in lightning current models. This standard also details the first and subsequent short strokes and how they can be simulated using the Heidler function.}
}
\newglossaryentry{lsm}
{
    name=Lightning stroke model,
    description={A mathematical model used to represent a lightning current waveshape. Examples of these are the Heidler function, the double exponential function and the approximation to the Heidler function that is represented in this dissertation.}
}
\newglossaryentry{short}
{
    name=Short stroke,
    description={A component of a lightning stroke that is impulsive in nature unlike the long stroke which is a comparatively long sustained current.}
}
\newglossaryentry{fs}
{
    name=First short stroke,
    description={A short stroke that is defined by the IEC~62305-1 as having a rise time of 10~\usec and a decay time of 350~\usec.}
}
\newglossaryentry{ss}
{
    name=Subsequent short stroke,
    description={A short stroke that is defined by the IEC~62305-1 as having a rise time of 0.25~\usec and a decay time of 100~\usec.}
}
\newglossaryentry{rtc}
{
    name=Rise time constant,
    description={A constant that is used to change the rise time of the lightning current waveshape.}
}
\newglossaryentry{dtc}
{
    name=Decay time constant,
    description={A constant that is used to change the decay time (the time to 50\% of peak current) of the lightning current waveshape.}
}
\newglossaryentry{rtf}
{
    name=Rise time function,
    description={The function that dictates what the shape of the rise of the waveshape is.}
}
\newglossaryentry{dtf}
{
    name=Decay time function,
    description={The function that dictates what the shape of the decay of the waveshape is.}
}
\newglossaryentry{steep}
{
    name=Waveshape steepness,
    description={A higher steepness in a waveshape results in a larger maximum instantaneous change in current.}
}
